---
title: "Survey Data Analysis Report"
author: "Group 14"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(survey)
library(knitr)
library(exactRankTests)
library(kableExtra)
library(gridExtra)
```

\newpage

# Introduction

Group members:  

- Jonas Neumair (11911064)
- Raphael Sperlich (11909380)
- David Baumgartner (11721765)

Topic: Physical activity and Productivity

Research questions we want to answer:  

1. Individuals who engage in regular physical activity will demonstrate a higher level of productivity in completing tasks for university or work compared to those who do not engage in regular physical activity.
2. Younger participants perform more physical activity per week than older ones.
3. Full-time students engage in more variety of physical activities (2+) compared to students who work.

## Load and clean data

To analyze the survey data effectively, we started by loading and renaming the columns. The data is loaded from a CSV file that was provided from our survey. We also set the column names to more readable titles: Gender, Age, Studies, NumberOfPhysicalActivityPerWeek, TypeOfPhysicalActivity, and WorkStudy.

```{r}
survey_data <- read.csv("group14.csv", header=TRUE)
names(survey_data) <- c("Gender", "Age", "Studies", 
                        "NumberOfPhysicalActivityPerWeek", 
                        "TypeOfPhysicalActivity", 
                        "WorkStudy")
```

Next, we need to separate the combined WorkStudy column into two distinct columns: ECTS and HoursOfWork. This was done because the question asked for a answer that combines the two.  

This is done using the `separate` function, with ";" as the delimiter. After splitting, we encounter values in the ECTS column use "," and "." as the floating point, which caused NA values with the coercion to numeric. To fix this, we applied `str_replace` to change to a uniform floating point character (".") representation. This step ensures that the ECTS values are in the correct numeric format. After coercion, we replace all NA values with 0 to avoid errors in later calculations.  

```{r}
survey_data <- separate(survey_data, 
                        "WorkStudy", 
                        c("ECTS", "HoursOfWork"), 
                        sep=";")

survey_data$ECTS <- as.numeric(str_replace(survey_data$ECTS, ",", "."))
survey_data$ECTS <- survey_data$ECTS %>% replace(is.na(.), 0)
```

We proceed to clean and convert the data in other columns. The HoursOfWork column is converted to a numeric type. For the NumberOfPhysicalActivityPerWeek column we handle non-numeric entries such as "Sunday" by replacing them with numeric values (e.g., "Sunday" is replaced with 1 because we assume the person meant that they do physical activity on a Sunday, meaning once a week) and then converting the column to numeric. Any remaining NA values in this column are filtered out so that our analysis is based on valid data entries.  

```{r warning=FALSE}
survey_data$HoursOfWork <- as.numeric(survey_data$HoursOfWork)

survey_data$NumberOfPhysicalActivityPerWeek <- as.numeric(
  survey_data$NumberOfPhysicalActivityPerWeek)

survey_data$NumberOfPhysicalActivityPerWeek <- 
  str_replace(survey_data$NumberOfPhysicalActivityPerWeek, "Sunday", "1")

survey_data$NumberOfPhysicalActivityPerWeek <- 
  as.numeric(survey_data$NumberOfPhysicalActivityPerWeek)

survey_data <- survey_data %>%
  filter(!is.na(NumberOfPhysicalActivityPerWeek))
```

To provide a more information on the participant's weekly time commitment, we calculate the WeeklyHours by combining the HoursOfWork with the study hours derived from ECTS credits. The conversion assumes 1 ECTS equals 25 hours of study over a 16-week semester. This step allows us to analyze the total weekly workload of each participant.  

```{r}
survey_data$HoursOfWork <- as.numeric(survey_data$HoursOfWork)
survey_data$WeeklyHours <- survey_data$HoursOfWork + ((survey_data$ECTS*25)/16)
```

We also create a selection of the relevant columns for the third question: NumberOfPhysicalActivityPerWeek, TypeOfPhysicalActivity, and HoursOfWork. This selection focuses our analysis on the key aspects related to physical activity and work commitments, providing a streamlined dataset for more detailed insights.

```{r}
r3_data <- survey_data %>%
  select(NumberOfPhysicalActivityPerWeek, TypeOfPhysicalActivity, HoursOfWork)
```

The described steps above results in the following table. The table is split into two chunks (by columns) due to the long column names.  

```{r echo=FALSE}
kable(
  head(survey_data[, c(1:4)]), 
  caption = "Survey data set (1/2)", 
  align = rep("c", 4),
  col.widths = rep("auto", ncol(survey_data))
)

kable(
  head(survey_data[, -c(1:4)]), 
  caption = "Survey data set (2/2)", 
  align = rep("c", 4),
  col.widths = rep("auto", ncol(survey_data))
)
```

## Outlier removal 

To handle outliers, we calculate the interquartile range (IQR) and filter out values outside the lower and upper bounds. We call this method "no outliers" throughout this document. 

```{r echo=FALSE}
Q1 <- quantile(survey_data$NumberOfPhysicalActivityPerWeek, 0.25, na.rm = TRUE)
Q3 <- quantile(survey_data$NumberOfPhysicalActivityPerWeek, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1

lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR

survey_data_no_outliers <- survey_data %>%
  filter(
    NumberOfPhysicalActivityPerWeek >= lower_bound & 
    NumberOfPhysicalActivityPerWeek <= upper_bound)
```

This is the table with removed outliers (split into chunks by columns).  

```{r echo=FALSE}
kable(
  head(survey_data_no_outliers[, c(1:4)]), 
  caption = "Data with removed outliers in physical activity (1/2)", 
  align = rep("c", 4),
  col.widths = rep("auto", ncol(survey_data_no_outliers))
)

kable(
  head(survey_data_no_outliers[, -c(1:4)]), 
  caption = "Data with removed outliers in physical activity (2/2)", 
  align = rep("c", 4),
  col.widths = rep("auto", ncol(survey_data_no_outliers))
)
```

For the transformed dataset, extreme values are scaled down by dividing them by 20, ensuring a more uniform distribution. We divide by 20 due to how we asked the question in the survey. We wanted to know how often people perform 20 minutes of physical exercise in a week. If the question is misinterpreted, one could answer with 60 instead of 3 for the question. This division corrects these outliers. We call this approach "transformed" throughout the document.    

```{r}
survey_data_transformed <- survey_data %>%
  mutate(NumberOfPhysicalActivityPerWeek = ifelse(
    NumberOfPhysicalActivityPerWeek < lower_bound | 
      NumberOfPhysicalActivityPerWeek > upper_bound,
    NumberOfPhysicalActivityPerWeek / 20,
    NumberOfPhysicalActivityPerWeek
  ))
```

This is the table with transformed values (split into chunks by columns).

```{r echo=FALSE}
kable(
  head(survey_data_transformed[, c(1:4)]), 
  caption = "Data with transformed physical activity (1/2)", 
  align = rep("c", 4),
  col.widths = rep("auto", ncol(survey_data_transformed))
)

kable(
  head(survey_data_transformed[, -c(1:4)]), 
  caption = "Data with transformed physical activity (2/2)", 
  align = rep("c", 4),
  col.widths = rep("auto", ncol(survey_data_transformed))
)
```

To analyse if younger participants perform more physical activity per week more precisely, we need to create at least two age groups. We will categorize the participants based on the median age. Splitting on the median should leave us with relatively balanced age groups. Ages larger than the median are set in the “over” and smaller in the “under” group. We are performing this categorization on the original and transformed data set.  

```{r}
survey_data_no_outliers$AgeGroup <- 
  as.factor(
    ifelse(survey_data_no_outliers$Age > median(survey_data_no_outliers$Age), 
         "over", "under")
  )

survey_data_transformed$AgeGroup <- 
  as.factor(
    ifelse(survey_data_transformed$Age > median(survey_data_transformed$Age), 
         "over", "under")
  )
```

With the data prepared, we can now answer our research questions.  

\newpage

# Research Question 1

Question we want to answer: "Individuals who engage in regular physical activity will demonstrate a higher level of productivity in completing tasks for university or work compared to those who do not engage in regular physical activity."  

To investigate the hypothesis that individuals who engage in regular physical activity demonstrate a higher level of productivity in completing tasks for university or work compared to those who do not, we perform an analysis in three main steps: Exploratory Data Analysis (EDA), Descriptive Inference, and Analytic Inference.

## Exploratory Data Analysis (EDA)

### Visualization for Research Question 1

We begin by visualizing the distribution of physical activity frequency among participants. This is done using a histogram that shows how often participants engage in physical activities per week

```{r echo=FALSE}
# Histogram of Physical Activity Frequency
ggplot(survey_data, aes(x = NumberOfPhysicalActivityPerWeek)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Physical Activity Frequency per Week",
       x = "Number of Physical Activities per Week",
       y = "Count")
```

### Comment on EDA

The histogram shows the distribution of how often participants engage in physical activities per week. This helps us understand the general trend and spread of physical activity frequency among participants. It can be seen that some numbers are quite high, this could be either due to the question being understood wrong or outliers. Both cases should be considered. Therefore we create 2 different dataframes, one that considers the outliers and eliminates them and one that transforms the values by dividing by 20. In the following you can see the two distributions


```{r}
ggplot(survey_data_no_outliers, aes(x = NumberOfPhysicalActivityPerWeek)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Physical Activity Frequency per Week",
       x = "Number of Physical Activities per Week",
       y = "Count")
```


```{r}
ggplot(survey_data_transformed, aes(x = NumberOfPhysicalActivityPerWeek)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Physical Activity Frequency per Week",
       x = "Number of Physical Activities per Week",
       y = "Count")
```

The histograms slightly differ. This is due to the transformation as more Data is available and therefore the distribution differs slightly.

## Descriptive Inference

### Summary Statistics

To gain insights, we compute summary statistics for both the transformed data and the dataset without outliers. This includes mean and standard deviation for ECTS and Hours of Work, grouped by the number of physical activities per week.

```{r echo=FALSE}
summary_stats_transformed <- survey_data_transformed %>%
  group_by(NumberOfPhysicalActivityPerWeek) %>%
  summarise(
    Mean_ECTS = mean(ECTS, na.rm = TRUE),
    Mean_HoursOfWork = mean(HoursOfWork, na.rm = TRUE),
    SD_ECTS = sd(ECTS, na.rm = TRUE),
    SD_HoursOfWork = sd(HoursOfWork, na.rm = TRUE)
  )

summary_stats_no_outliers <- survey_data_no_outliers %>%
  group_by(NumberOfPhysicalActivityPerWeek) %>%
  summarise(
    Mean_ECTS = mean(ECTS, na.rm = TRUE),
    Mean_HoursOfWork = mean(HoursOfWork, na.rm = TRUE),
    SD_ECTS = sd(ECTS, na.rm = TRUE),
    SD_HoursOfWork = sd(HoursOfWork, na.rm = TRUE)
  )
```

The summary statistics tables provide a detailed view of how physical activity correlates with productivity measures.

```{r}
kable(summary_stats_transformed, 
      caption = "Summary statistics transformed data")
```

In the summary we cannot immediately see the a positive relationship between the productivity and the hours of work. 

```{r}
kable(summary_stats_no_outliers, 
      caption = "Summary statistics no outliers in physical activities")
```

## Analytic Inference

### Hypothesis Testing

To test our hypothesis we create linear models that check if a higher number of physical activities per week results in more work output.

```{r echo=FALSE}

model_transformed_ects <- lm(ECTS ~ NumberOfPhysicalActivityPerWeek, data = survey_data_transformed)
summary(model_transformed_ects)

model_no_outliers_ects <- lm(ECTS ~ NumberOfPhysicalActivityPerWeek, data = survey_data_no_outliers)
summary(model_no_outliers_ects)

model_transformed_HoursOfWork <- lm(HoursOfWork ~ NumberOfPhysicalActivityPerWeek, data = survey_data_transformed)
summary(model_transformed_HoursOfWork)

model_no_outliers_HoursOfWork <- lm(HoursOfWork ~ NumberOfPhysicalActivityPerWeek, data = survey_data_no_outliers)
summary(model_no_outliers_HoursOfWork)

model_transformed_WeeklyHours <- lm(WeeklyHours ~ NumberOfPhysicalActivityPerWeek, data = survey_data_transformed)
summary(model_transformed_HoursOfWork)

model_no_outliers_WeeklyHours <- lm(WeeklyHours ~ NumberOfPhysicalActivityPerWeek, data = survey_data_no_outliers)
summary(model_no_outliers_HoursOfWork)
```

The linear models examining ECTS and Hours of Work relative to weekly physical activities indicate a positive relationship but no statistical significance. Both ECTS models indicate a positive trend, yet fail to reach significance (p = 0.149 and p = 0.233). Similarly, the Hours of Work models show coefficients that are not statistically different from zero (p = 0.581 and p = 0.533). These results suggest that while there may be trends suggesting more physical activity correlates with higher productivity measures, further data is necessary to confirm a statistical significance.


```{r echo=FALSE}
# Create a scatterplot of ECTS vs. NumberOfPhysicalActivityPerWeek with regression line
 plot1 <- ggplot(survey_data_no_outliers, aes(x = NumberOfPhysicalActivityPerWeek, y = ECTS)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "Scatterplot of ECTS vs. Number of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "ECTS Credits") +
  theme_minimal()

  plot2 <- ggplot(survey_data_transformed, aes(x = NumberOfPhysicalActivityPerWeek, y = ECTS)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "ECTS vs. \nNumber of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "ECTS Credits") +
  theme_minimal()

  plot3 <- ggplot(survey_data_transformed, aes(x = NumberOfPhysicalActivityPerWeek, y = WeeklyHours)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "Total weekly hours vs.\nNumber of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "Composite Productivity (Hours of Work + ECTS)") +
  theme_minimal()
  plot4 <- ggplot(survey_data_no_outliers, aes(x = NumberOfPhysicalActivityPerWeek, y = WeeklyHours)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "Composite Productivity vs. Number of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "Composite Productivity (Hours of Work + ECTS)") +
  theme_minimal()

grid.arrange(plot2,plot3, ncol=2)
```

These visualizations reinforce the conclusion that while there are trends indicating a positive relationship between physical activity and productivity, these are not statistically significant. Note: We plotted only two graphs as the difference between no outliers and transformed data was negligible and would not strengthen nor weaken the argument.

\newpage

# Research Question 2

Question we want to answer: "Younger participants perform more physical activity per week than older ones."  

## Exploratory data analysis

To get a first impression, we can begin by checking the change in the number of physical activities per week with increasing age. We continue using the data frames `survey_data_no_outliers` and `survey_data_transformed` because we are again researching the attribute number of physical activities per week.   

```{r}
survey_data_grouped_age <- survey_data_no_outliers %>%
  group_by(Age) %>%
  summarise(Mean_PhysicalActivity = mean(NumberOfPhysicalActivityPerWeek))

ggplot(survey_data_grouped_age, aes(x = Age, y = Mean_PhysicalActivity)) +
  geom_col(fill = "blue", color = "black") +
  geom_vline(xintercept = median(survey_data_grouped_age$Age), 
             linetype = "dashed", 
             color = "red") +
  annotate("text", 
           x=median(survey_data_grouped_age$Age)+1, 
           y=4, 
           label="Median age", 
           angle=90, 
           color="red") +
  labs(title = "Mean number of physical activity in a week per age",
       x = "Age",
       y = "Mean number of physical activity per week")
```

The plot shows, that we have some missing ages across our survey data - mostly with age values above the median age. We can also see, that we have the highest mean with age 45. With this plot, it is not very clear if younger participants perform more physical activities but it seems like "younger" (age < median) participants participate in more physical activities.  

We can combine both methods into one data frame for easier plotting.  

```{r}
survey_data_combined <- tibble(
  AgeGroup = c(survey_data_transformed$AgeGroup, 
               survey_data_no_outliers$AgeGroup),
  
  PhysicalActivity = c(survey_data_transformed$NumberOfPhysicalActivityPerWeek, 
                       survey_data_no_outliers$NumberOfPhysicalActivityPerWeek),
  
  Method = c(rep("Transformed", length(survey_data_transformed$AgeGroup)),
             rep("No Outlier", length(survey_data_no_outliers$AgeGroup)))
)
```

We can check how balanced our two age groups are.  

```{r}
ggplot(survey_data_combined, aes(x = AgeGroup, fill = AgeGroup)) +
  geom_bar(stat="count", color = "black") +
  labs(title = "Balance of observations per age group",
       x = "Age group",
       y = "Count") +
  facet_wrap(~ Method) +
  theme(legend.position = "none")
```

The plots show, that we have a perfect balance in the "no outlier" and a slight imbalance in the "transformed" approach. The imbalance could influence the hypothesis tests.    

We can visualize both groups by grouping the age group and computing the mean on the number of physical activities per week. This can give us a good first impression if we have a difference in the groups. We start with the bar plots for the data without outliers.  

```{r}
data_outlier_agegroup <- survey_data_no_outliers %>%
  group_by(AgeGroup) %>%
  summarise(mean_PhysicalActivity = mean(NumberOfPhysicalActivityPerWeek, 
                                         na.rm = TRUE))

ggplot(data_outlier_agegroup, 
  aes(x = AgeGroup, y = mean_PhysicalActivity, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(title = "Change of mean number of physical activity per week per age",
       subtitle = "with no outlier data",
       x = "Age",
       y = "Mean number of physical activity per week") +
  theme(legend.position = "none")
```

We also check the transformed data.  

```{r}
data_transformed_agegroup <- survey_data_transformed %>%
  group_by(AgeGroup) %>%
  summarise(mean_PhysicalActivity = mean(NumberOfPhysicalActivityPerWeek, 
                                         na.rm = TRUE))

ggplot(data_transformed_agegroup, 
  aes(x = AgeGroup, y = mean_PhysicalActivity, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(title = "Change of mean number of physical activity per week per age",
       subtitle = "with transformed data",
       x = "Age",
       y = "Mean number of physical activity per week") +
  theme(legend.position = "none")
```

The exploratory data analysis indicates a difference in the number of physical activities between age groups. With plots alone, we cannot prove nor disprove if the hypothesis is true. We need to verify, if the results are significant and did not happen just by chance. So, we will check summary statistics and then apply hypothesis tests.  

## Descriptive Inference

### Summary statistics

We, again gather statistical information with mean, median and standard deviation in number of physical activities per week with grouped age group.  

```{r echo=FALSE}
summary_stats_transformed_rq2 <- survey_data_transformed %>%
  group_by(AgeGroup) %>%
  summarise(
    Mean_physical = mean(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
    Median_physical = median(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
  )

summary_stats_no_outliers_rq2 <- survey_data_no_outliers %>%
  group_by(AgeGroup) %>%
  summarise(
    Mean_physical = mean(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
    Median_physical = median(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
  )
```

We, can combine the metrics into one data frame and visualize the results for both methods (no outliers and transformed).  

```{r}
# combine into one df
summary_stats_rq2 <- tibble(
  AgeGroup = c(summary_stats_no_outliers_rq2$AgeGroup, 
               summary_stats_transformed_rq2$AgeGroup),
  
  Mean = c(summary_stats_no_outliers_rq2$Mean_physical, 
           summary_stats_transformed_rq2$Mean_physical),
  
  Median = c(summary_stats_no_outliers_rq2$Median_physical, 
             summary_stats_transformed_rq2$Median_physical),
  
  Method = c(rep("Transform", length(summary_stats_no_outliers_rq2$AgeGroup)), 
             rep("No Outlier", length(summary_stats_transformed_rq2$AgeGroup)))
)
```

After combining the metrics into one data frame, we can plot for median and mean and compare our methods to handle outliers ("transformed" and "no outlier").  

```{r}
ggplot(summary_stats_rq2, aes(x = AgeGroup, y = Median, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(
    title = "Median number of physical activities in age groups per methods",
    x = "Age groups",
    y = "Median") +
  theme(legend.position = "none") +
  facet_wrap(~ Method)
```

```{r}
ggplot(summary_stats_rq2, aes(x = AgeGroup, y = Mean, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(
    title = "Mean number of physical activities in age groups per methods",
    x = "Age groups",
    y = "Mean") +
  theme(legend.position = "none") +
  facet_wrap(~ Method)
```

The plots of statistical metrics show us, that the "under" group constantly has higher values compared to the "over" age group. This indicates that our hypothesis could hold that "younger" participants perform more physical activity compared to "older" ones.  

As a visualization, we chose a boxplot, since this can show us the difference of the groups via the distribution of the values with faceting to allow us to compare "no outliers" to the "transformed" approach.  

```{r}
ggplot(survey_data_combined, 
       aes(x = AgeGroup, 
           y = PhysicalActivity, 
           fill = AgeGroup)) +
  geom_boxplot() +
  labs(
    title = "Distribution of physical activities per week by age group",
    x = "Age Group", 
    y = "Activities per Week") +
  facet_wrap(~ Method) +
  theme(legend.position = "none")
```

Here, we can see, that the difference of "under" and "over" is smaller with the "no outliers" approach. Still, both methods show a visual difference between the groups.  

## Analytic Inference

To test if our results are not just by chance, we need to perform hypothesis tests. When the data in the groups is normally distributed, we can use an independent t-test, otherwise, we can use the Mann-Whitney U Test.  

### Test for nomal distribution

We chose to test the distribution with the Shapiro-Wilk Test. In our case, we apply the test to see if the number of physical activity per week follows a normal distribution for "under" and "over" age groups. We define a confidence value of "0.05", to accept or reject the null hypothesis, which says the sample is following a normal distribution.  

```{r}
shapiro.test(
  survey_data_transformed$NumberOfPhysicalActivityPerWeek[
    survey_data_transformed$AgeGroup == "under"]
  )

shapiro.test(
  survey_data_transformed$NumberOfPhysicalActivityPerWeek[
    survey_data_transformed$AgeGroup == "over"]
  )
```

For the transformed data set, we can see, that number of physical activities in the group "under" does not follow a normal distribution (p-value < 0.05 &rarr reject null hypothesis).  

```{r}
shapiro.test(
  survey_data_no_outliers$NumberOfPhysicalActivityPerWeek[
    survey_data_no_outliers$AgeGroup == "under"]
  )

shapiro.test(
  survey_data_no_outliers$NumberOfPhysicalActivityPerWeek[
    survey_data_no_outliers$AgeGroup == "over"]
  )
```

For the method "no outliers", we can see that the values in the group "over" also do not follow a normal distribution.   

### Hypothesis testing

Since, our groups do not follow a normal distribution, we need to apply a different significance test. We chose to use the Mann-Whitney U Test.

```{r}
wilcox.test(
  NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
  data = survey_data_transformed
)

wilcox.test(
  NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
  data = survey_data_no_outliers
)
```

The test shows for both methods a p-value larger than "0.05". Therefore, we do not have a significant difference between groups "over" and "under". The warning in the code indicates, that the exact p-value could not be computed due to ties in the rank. So, to make sure we can prove or disprove a significant difference, we use a linear model and evaluate the results.  

```{r}
model_transformed_rq2 <- lm(NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
                     data = survey_data_transformed)
summary(model_transformed_rq2)

model_outliers_rq2 <- lm(NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
                     data = survey_data_no_outliers)
summary(model_outliers_rq2)
```

With the method "transformed" we almost have a significant impact of the "under" age group on physical activities per week, but the p-value is still above our threshold of "0.05". Meaning, we need to keep the null hypothesis that we do not have a significant correlation between the number of physical activities per week and the age group.  

## Evaluation

The plots in the EDA indicated, that we have a difference between age groups and that "younger" participants have more active days in a week compared to "older" ones. Statistical summaries further showed the same results as the EDA investigation. But after evaluating the significance tests, we can say that there is no significant evidence for our second research question.  

\newpage

# Research question 3

Question we want to answer: "Full-time students engage in more variety of physical activities (2+) compared to students who work."  

## Exploratory Data Analysis

We load the file.
In order to answer R3 we need to define who is a Full-time student and who is a Working student.

```{r student-types}
r3_data <- r3_data %>%
  mutate(Category = if_else(HoursOfWork==0, 
                            "Full-Time Student", 
                            "Working Student"))

r3_data %>%
  ggplot(aes(x=Category, fill=Category)) +
  geom_histogram(stat = "count", color = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.2, size = 5) +
  labs(
    title = "Number of Full-Time Students and Working Students",
    x = "Category",
    y = "Count"
  ) +
  theme(legend.position = "none")
```

Since the comparison between Full-Time Students and Working Students is not very balanced, we try to create sub groups to make the comparison groups more clear.  

```{r sub-category}
r3_data <- r3_data %>%
  mutate(SubCategory = case_when(
    HoursOfWork == 0 ~ "0",
    0 != HoursOfWork & HoursOfWork <= 10 ~ "1-10h",
    10 < HoursOfWork & HoursOfWork <= 20 ~ "11-20h",
    20 < HoursOfWork & HoursOfWork <= 30 ~ "21-30h",
    30 < HoursOfWork ~ "30h+"
  ))

r3_data %>%
  ggplot(aes(x=SubCategory, fill=SubCategory)) +
  geom_histogram(stat = "count", color = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.2, size = 5) +
  labs(
    title = "Number of students based on SubCategory",
    x = "SubCategory",
    y = "Count"
  ) +
  theme(legend.position = "none")
```
In addition we need to extract the different activities to sum up the amount of different physical activities each person is performing.

```{r physical-variety}
types_of_physcial_activity <- c("StrengthTraining", 
                                "Cardio", 
                                "RecreationalActivities", 
                                "BallSports", 
                                "FlexibilityAndMobilit", 
                                "MartialArt", 
                                "Other")

r3_data <- r3_data %>%
  mutate(
    StrengthTraining = if_else(
      str_detect(TypeOfPhysicalActivity, "Strength Training"), 1, 0),
    Cardio = if_else(
      str_detect(TypeOfPhysicalActivity, "Cardio"), 1, 0),
    RecreationalActivities = if_else(
      str_detect(TypeOfPhysicalActivity, "Recreational Activities"), 1, 0),
    BallSports = if_else(
      str_detect(TypeOfPhysicalActivity, "Ball Sports"), 1, 0),
    FlexibilityAndMobilit = if_else(
      str_detect(TypeOfPhysicalActivity, "Flexibility and Mobilit"), 1, 0),
    MartialArt = if_else(
      str_detect(TypeOfPhysicalActivity, "Martial Art"), 1, 0),
    Other = if_else(
      str_detect(TypeOfPhysicalActivity, "Other"), 1, 0)
  ) %>%
  select(-TypeOfPhysicalActivity)

r3_data <- r3_data %>%
  mutate(
    NumberOfDifferentActivity = rowSums(r3_data[, types_of_physcial_activity])
  )
```

## Descriptive Inference

We calculate the mean of the number of different activity to compare the results for R3.

```{r mean-full-working}
r3_mean_category <- r3_data %>%
  group_by(Category) %>%
  summarize(
    MeanNumberOfDifferentActivity=mean(NumberOfDifferentActivity)
  )

kable(
  r3_mean_category, 
  caption = "Mean number of different activities for two categories"
)
```

```{r}
r3_mean_subcategory <- r3_data %>%
  group_by(SubCategory) %>%
  summarize(
    MeanNumberOfDifferentActivity=mean(NumberOfDifferentActivity)
  )

kable(
  r3_mean_subcategory, 
  caption = "Mean number of different activities for subcategories"
)
```

## Analytic Inference

At first we check if our data has normal distribution.

```{r}
shapiro.test(
  r3_data$NumberOfDifferentActivity[r3_data$Category == "Full-Time Student"])

shapiro.test(
  r3_data$NumberOfDifferentActivity[r3_data$Category == "Working Student"])
```

Since it is not, we can use the Mann-Whitney/Wilcoxon test to check if we can accept or reject our H0.

H0 - There is no significant difference in the number of physical activity between full-time students and working students.
H1 - There is significant difference in the number of physical activity between full-time students and working students.

A value of < 0.05 means that we can reject the null hypotheses and accept our R3.

```{r}
p_value_base <- wilcox.test(NumberOfDifferentActivity ~ Category, data = r3_data)
p_value_base
```

Since the value is above 0.05, we can't reject H0, meaning that R3 is rejected.

However, we already created subcategories to further specify the working students group to see, if there is a subgroup, for which the R3 holds.

```{r}
r3_data$SubCategory <- as.factor(r3_data$SubCategory)

r3_group1 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="1-10h")

r3_group2 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="11-20h")

r3_group3 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="21-30h")

r3_group4 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="30h+")

p_value_group1 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, 
                               data = r3_group1, exact = TRUE)
p_value_group2 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, 
                               data = r3_group2, exact = TRUE)
p_value_group3 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, 
                               data = r3_group3, exact = TRUE)
p_value_group4 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, 
                               data = r3_group4, exact = TRUE)

df <- data.frame(
  group = c("Full-Time Student vs. Working Student", 
            "1-10h", "11-20h", 
            "21-30h", 
            "30h+"),
  p_value = c(p_value_base$p.value, 
              p_value_group1$p.value, 
              p_value_group2$p.value, 
              p_value_group3$p.value, 
              p_value_group4$p.value)
)

kable(
  df,
  caption = "p-values for different groups of study/work balance"
)
```

We can see that only one group rejects the null hypothesis. If we can compare full-time students with students working more than 30h we can see a significant difference in the number of different physical activities.
