---
title: "Survey Data Analysis Report"
author: "Group 14"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(survey)
library(knitr)
library(exactRankTests)
```

\newpage

# Introduction

Group members:  

- Jonas Neumair (11911064)
- Raphael Sperlich (11909380)
- David Baumgartner (11721765)

Topic: Physical activity and Productivity

Research questions we want to answer:  

1. Individuals who engage in regular physical activity will demonstrate a higher level of productivity in completing tasks for university or work compared to those who do not engage in regular physical activity.
2. Younger participants perform more physical activity per week than older ones.
3. Full-time students engage in more variety of physical activities (2+) compared to students who work.

## Prepare data

```{r cars}
# Load the survey data
survey_data <- read.csv("group14.csv", header=TRUE)
names(survey_data) <- c("Gender", "Age", "Studies", 
                        "NumberOfPhysicalActivityPerWeek", 
                        "TypeOfPhysicalActivity", 
                        "WorkStudy")

# Split WorkStudy into ECTS and HoursOfWork
survey_data <- separate(survey_data, 
                        "WorkStudy", 
                        c("ECTS", "HoursOfWork"), sep=";")

# unify different comma representations for ECTS before coercion
survey_data$ECTS <- as.numeric(sub(",", ".", survey_data$ECTS, fixed = TRUE))
survey_data$HoursOfWork <- as.numeric(survey_data$HoursOfWork)
survey_data$NumberOfPhysicalActivityPerWeek <- as.numeric(
  survey_data$NumberOfPhysicalActivityPerWeek)

# Display the data
kable(head(survey_data), caption = "Survey data set")
```

With the data prepared, we can now answer our research questions.  

\newpage

# Research Question 1

## Exploratory Data Analysis (EDA)

### Visualization for Research Question 1

```{r echo=FALSE}
# Histogram of Physical Activity Frequency
ggplot(survey_data, aes(x = NumberOfPhysicalActivityPerWeek)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Physical Activity Frequency per Week",
       x = "Number of Physical Activities per Week",
       y = "Count")
```
### Comment on EDA

The histogram shows the distribution of how often participants engage in physical activities per week. This helps us understand the general trend and spread of physical activity frequency among participants. It can be seen that some numbers are quite high, this could be either due to the question being understood wrong or outliers. Both cases should be considered. Therefore we create 2 different dataframes, one that considers the outliers and eliminates them and one that transforms the values by %20. 

### Outlier removal 

```{r echo=FALSE}
Q1 <- quantile(survey_data$NumberOfPhysicalActivityPerWeek, 0.25, na.rm = TRUE)
Q3 <- quantile(survey_data$NumberOfPhysicalActivityPerWeek, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1

lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR

survey_data_no_outliers <- survey_data %>%
  filter(NumberOfPhysicalActivityPerWeek >= lower_bound & NumberOfPhysicalActivityPerWeek <= upper_bound)

kable(head(survey_data_no_outliers), 
      caption = "Data with removed outliers in physical activity")
```

```{r}
ggplot(survey_data_no_outliers, aes(x = NumberOfPhysicalActivityPerWeek)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Physical Activity Frequency per Week",
       x = "Number of Physical Activities per Week",
       y = "Count")
```

### Outlier removal 

```{r echo=FALSE}
Q1 <- quantile(survey_data$NumberOfPhysicalActivityPerWeek, 0.25, na.rm = TRUE)
Q3 <- quantile(survey_data$NumberOfPhysicalActivityPerWeek, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1

lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR

survey_data_transformed <- survey_data %>%
  mutate(NumberOfPhysicalActivityPerWeek = ifelse(
    NumberOfPhysicalActivityPerWeek < lower_bound | NumberOfPhysicalActivityPerWeek > upper_bound,
    NumberOfPhysicalActivityPerWeek / 20,
    NumberOfPhysicalActivityPerWeek
  ))

kable(head(survey_data_transformed), 
      caption = "Data with transformed physical activity")

# transofrm ects to work hours per week
survey_data_transformed <- survey_data_transformed %>%
  mutate(hours_of_work_ects = ECTS * 25 / 16)
survey_data_no_outliers <- survey_data_no_outliers %>%
  mutate(hours_of_work_ects = ECTS * 25 / 16)
# Create the composite measure
survey_data_transformed <- survey_data_transformed %>%
  mutate(CompositeProductivity = hours_of_work_ects + HoursOfWork)

survey_data_no_outliers <- survey_data_no_outliers %>%
  mutate(CompositeProductivity = hours_of_work_ects + HoursOfWork)
```

```{r}
ggplot(survey_data_transformed, aes(x = NumberOfPhysicalActivityPerWeek)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Physical Activity Frequency per Week",
       x = "Number of Physical Activities per Week",
       y = "Count")
```

## Descriptive Inference

### Summary Statistics

```{r echo=FALSE}
summary_stats_transformed <- survey_data_transformed %>%
  group_by(NumberOfPhysicalActivityPerWeek) %>%
  summarise(
    Mean_ECTS = mean(ECTS, na.rm = TRUE),
    Mean_HoursOfWork = mean(HoursOfWork, na.rm = TRUE),
    SD_ECTS = sd(ECTS, na.rm = TRUE),
    SD_HoursOfWork = sd(HoursOfWork, na.rm = TRUE)
  )
summary_stats_no_outliers <- survey_data_no_outliers %>%
  group_by(NumberOfPhysicalActivityPerWeek) %>%
  summarise(
    Mean_ECTS = mean(ECTS, na.rm = TRUE),
    Mean_HoursOfWork = mean(HoursOfWork, na.rm = TRUE),
    SD_ECTS = sd(ECTS, na.rm = TRUE),
    SD_HoursOfWork = sd(HoursOfWork, na.rm = TRUE)
  )
```

```{r}
kable(summary_stats_transformed, 
      caption = "Summary statistics transformed data")
```

```{r}
kable(summary_stats_no_outliers, 
      caption = "Summary statistics no outliers in physical activities")
```

## Analytic Inference

### Hypothesis Testing

```{r echo=FALSE}

model_transformed_ects <- lm(ECTS ~ NumberOfPhysicalActivityPerWeek, data = survey_data_transformed)
summary(model_transformed_ects)

model_no_outliers_ects <- lm(ECTS ~ NumberOfPhysicalActivityPerWeek, data = survey_data_no_outliers)
summary(model_no_outliers_ects)

model_transformed_HoursOfWork <- lm(HoursOfWork ~ NumberOfPhysicalActivityPerWeek, data = survey_data_transformed)
summary(model_transformed_HoursOfWork)

model_no_outliers_HoursOfWork <- lm(HoursOfWork ~ NumberOfPhysicalActivityPerWeek, data = survey_data_no_outliers)
summary(model_no_outliers_HoursOfWork)

model_transformed_HoursOfWork <- lm(NumberOfPhysicalActivityPerWeek ~ CompositeProductivity, data = survey_data_transformed)
summary(model_transformed_HoursOfWork)

model_no_outliers_HoursOfWork <- lm(  NumberOfPhysicalActivityPerWeek ~ CompositeProductivity, data = survey_data_no_outliers)
summary(model_no_outliers_HoursOfWork)

```

```{r echo=FALSE}

survey_design_no_outliers <- svydesign(id = ~1, data = survey_data_no_outliers, weights = ~1)
model_original <- svyglm(ECTS ~ NumberOfPhysicalActivityPerWeek + HoursOfWork, design = survey_design_no_outliers)
summary(model_original)

survey_design_transformed <- svydesign(id = ~1, data = survey_data_transformed, weights = ~1)
model_transformed <- svyglm(ECTS ~ NumberOfPhysicalActivityPerWeek + HoursOfWork, design = survey_design_transformed)
summary(model_transformed)
```

```{r echo=FALSE}
# Create a scatterplot of ECTS vs. NumberOfPhysicalActivityPerWeek with regression line
ggplot(survey_data_no_outliers, aes(x = NumberOfPhysicalActivityPerWeek, y = ECTS)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "Scatterplot of ECTS vs. Number of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "ECTS Credits") +
  theme_minimal()

ggplot(survey_data_transformed, aes(x = NumberOfPhysicalActivityPerWeek, y = ECTS)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "Scatterplot of ECTS vs. Number of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "ECTS Credits") +
  theme_minimal()

ggplot(survey_data_transformed, aes(x = NumberOfPhysicalActivityPerWeek, y = CompositeProductivity)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "Scatterplot of Composite Productivity vs. Number of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "Composite Productivity (Hours of Work + ECTS)") +
  theme_minimal()
ggplot(survey_data_no_outliers, aes(x = NumberOfPhysicalActivityPerWeek, y = CompositeProductivity)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, color = "blue") +
  labs(title = "Scatterplot of Composite Productivity vs. Number of Physical Activities per Week",
       x = "Number of Physical Activities per Week",
       y = "Composite Productivity (Hours of Work + ECTS)") +
  theme_minimal()

```

\newpage

# Research Question 2

## Exploratory data analysis

To get a first impression, we can first check the change of the number of physical activity per week with increasing age. We continue using the data frames `survey_data_no_outliers` and `survey_data_transformed` because are again researching on the attribute number of physical activities per week.  

```{r}
survey_data_grouped_age <- survey_data_no_outliers %>%
  group_by(Age) %>%
  summarise(Mean_PhysicalActivity = mean(NumberOfPhysicalActivityPerWeek))

ggplot(survey_data_grouped_age, aes(x = Age, y = Mean_PhysicalActivity)) +
  geom_col(fill = "blue", color = "black") +
  geom_vline(xintercept = median(survey_data_grouped_age$Age), 
             linetype = "dashed", 
             color = "red") +
  annotate("text", 
           x=median(survey_data_grouped_age$Age)+1, 
           y=4, 
           label="Median age", 
           angle=90, 
           color="red") +
  labs(title = "Mean number of physical activity in a week per age",
       x = "Age",
       y = "Mean number of physical activity per week")
```

The plot shows, that we have some missing ages across the whole survey data - mostly with age values larger then the median age. We can also see, that we have the largest mean with age 45. With this plot, it is not very clear if younger participants really perform more physical activities but it seems like "younger" (age < median) participants participate in more physical activities.  

In order to analyse if younger participants perform more physical activity per week more precisely, we need to create at least two age groups. We will categorize the participants based on the median age. Splitting on the median should leave us with relatively balanced groups in the age groups. Ages larger as the median are set in the "over" and smaller ones in the "under" group. We are performing this categorization on the original and transformed data set.  

```{r}
# no outlier survey data set
survey_data_no_outliers$AgeGroup <- 
  as.factor(
    ifelse(survey_data_no_outliers$Age > median(survey_data_no_outliers$Age), 
         "over", "under")
  )

# transformed survey data set
survey_data_transformed$AgeGroup <- 
  as.factor(
    ifelse(survey_data_transformed$Age > median(survey_data_transformed$Age), 
         "over", "under")
  )
```

We can combine both methods into one data frame for easier plotting.  

```{r}
survey_data_combined <- tibble(
  AgeGroup = c(survey_data_transformed$AgeGroup, 
               survey_data_no_outliers$AgeGroup),
  
  PhysicalActivity = c(survey_data_transformed$NumberOfPhysicalActivityPerWeek, 
                       survey_data_no_outliers$NumberOfPhysicalActivityPerWeek),
  
  Method = c(rep("Transformed", length(survey_data_transformed$AgeGroup)),
             rep("No Outlier", length(survey_data_no_outliers$AgeGroup)))
)
```

We can check how balanced our two age groups are.  

```{r}
ggplot(survey_data_combined, aes(x = AgeGroup, fill = AgeGroup)) +
  geom_bar(stat="count", color = "black") +
  labs(title = "Balance of observations per age group",
       x = "Age group",
       y = "Count") +
  facet_wrap(~ Method) +
  theme(legend.position = "none")
```

The plots shows, that we have perfect balance in the "no outlier" and a slight inbalance in "tranformed" approach. The inbalance could influence the hypothesis tests.    

We can visualize both groups by grouping the age group and computing the mean of number of physical activities. This can give us a good first impression if we have a difference in the groups. We start with the bar plots for the data without outliers.   

```{r}
data_outlier_agegroup <- survey_data_no_outliers %>%
  group_by(AgeGroup) %>%
  summarise(mean_PhysicalActivity = mean(NumberOfPhysicalActivityPerWeek, 
                                         na.rm = TRUE))

ggplot(data_outlier_agegroup, 
  aes(x = AgeGroup, y = mean_PhysicalActivity, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(title = "Change of mean number of physical activity per week per age",
       subtitle = "with no outlier data",
       x = "Age",
       y = "Mean number of physical activity per week") +
  theme(legend.position = "none")
```

We also check the transformed data.  

```{r}
data_transformed_agegroup <- survey_data_transformed %>%
  group_by(AgeGroup) %>%
  summarise(mean_PhysicalActivity = mean(NumberOfPhysicalActivityPerWeek, 
                                         na.rm = TRUE))

ggplot(data_transformed_agegroup, 
  aes(x = AgeGroup, y = mean_PhysicalActivity, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(title = "Change of mean number of physical activity per week per age",
       subtitle = "with transformed data",
       x = "Age",
       y = "Mean number of physical activity per week") +
  theme(legend.position = "none")
```

The exploratory data analysis indicates that we have a difference in number of physical activities between age groups. With plots alone, we cannot proof nor disproof if the hypothesis is true. We need to check, if the results are significant and did not happen just by chance. So, we will check summary statistics and then apply hypothesis tests.  

## Descriptive Inference

### Summary statistics

We, again gather statistical information with mean, median and standard deviation in number of physical activities per week with grouped age group.  

```{r echo=FALSE}
summary_stats_transformed_rq2 <- survey_data_transformed %>%
  group_by(AgeGroup) %>%
  summarise(
    Mean_physical = mean(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
    Median_physical = median(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
  )

summary_stats_no_outliers_rq2 <- survey_data_no_outliers %>%
  group_by(AgeGroup) %>%
  summarise(
    Mean_physical = mean(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
    Median_physical = median(NumberOfPhysicalActivityPerWeek, na.rm = TRUE),
  )
```

We, can combine the metrics into one data frame and visualize the results for both methods (no outliers and transformed).  

```{r}
# combine into one df
summary_stats_rq2 <- tibble(
  AgeGroup = c(summary_stats_no_outliers_rq2$AgeGroup, 
               summary_stats_transformed_rq2$AgeGroup),
  
  Mean = c(summary_stats_no_outliers_rq2$Mean_physical, 
           summary_stats_transformed_rq2$Mean_physical),
  
  Median = c(summary_stats_no_outliers_rq2$Median_physical, 
             summary_stats_transformed_rq2$Median_physical),
  
  Method = c(rep("Transform", length(summary_stats_no_outliers_rq2$AgeGroup)), 
             rep("No Outlier", length(summary_stats_transformed_rq2$AgeGroup)))
)
```



```{r}
ggplot(summary_stats_rq2, aes(x = AgeGroup, y = Median, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(
    title = "Median number of physical activities in age groups per methods",
    x = "Age groups",
    y = "Median") +
  theme(legend.position = "none") +
  facet_wrap(~ Method)
```

```{r}
ggplot(summary_stats_rq2, aes(x = AgeGroup, y = Mean, fill = AgeGroup)) +
  geom_col(color = "black") +
  labs(
    title = "Mean number of physical activities in age groups per methods",
    x = "Age groups",
    y = "Mean") +
  theme(legend.position = "none") +
  facet_wrap(~ Method)
```

The plots of statistical metrics show us, that the "under" group constantly has higher values compare to the "over" age group. This indicates that our hypothesis could hold that "younger" participants perform more sport compared to "older" ones.  

As a visualization we chose a boxplot, since this can show us the difference of the groups via the distribution of the values with faceting to allow us to compare "no outliers" to "transformed" approach.    

```{r}
ggplot(survey_data_combined, 
       aes(x = AgeGroup, 
           y = PhysicalActivity, 
           fill = AgeGroup)) +
  geom_boxplot() +
  labs(
    title = "Distribution of physical activities per week by age group",
    x = "Age Group", 
    y = "Activities per Week") +
  facet_wrap(~ Method) +
  theme(legend.position = "none")
```

Here, we can see, that the difference of "under" and "over" is smaller with the "no outliers" approach. Still, both methods show a visual difference between the groups.  

## Analytic Inference

To test if our results are not just by chance, we need to perform hypothesis tests. When the data in the groups is normally distributed, we can use a independent t-test, otherwise we can use the Mann-Whitney U Test.  

### Test for nomal distribution

We chose to test the distribution with the Shapiro-Wilk Test. In our case we apply the test to see if number of physical activity per week is following a normal distribution for "under" and "over" age groups. We define a confidence value of `0.05`, to accept or reject the null hypothesis, which says the sample is following a normal distribution.   

```{r}
shapiro.test(
  survey_data_transformed$NumberOfPhysicalActivityPerWeek[survey_data_transformed$AgeGroup == "under"])

shapiro.test(
  survey_data_transformed$NumberOfPhysicalActivityPerWeek[survey_data_transformed$AgeGroup == "over"])
```

For the transformed data set, we can see, that number of physical activities in the group "under" does not follow a normal distribution (p-value < 0.05 &rarr reject null hypothesis).  


```{r}
shapiro.test(
  survey_data_no_outliers$NumberOfPhysicalActivityPerWeek[survey_data_no_outliers$AgeGroup == "under"])

shapiro.test(
  survey_data_no_outliers$NumberOfPhysicalActivityPerWeek[survey_data_no_outliers$AgeGroup == "over"])
```

For the method "no outliers", we can see that the values in the group "over" also do not follow a normal distribution.   

### Hypothesis testing

Since, our groups do not follow a normal distribution, we need to apply a different significance test. We chose to use the Mann-Whitney U Test.

```{r}
wilcox.test(
  NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
  data = survey_data_transformed
)

wilcox.test(
  NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
  data = survey_data_no_outliers
)
```

The test shows for both method a p-value larger then 0.05 and therefore, we do not have significant difference between groups "over" and "under". The warning in the code indicates, that the exact p-value could not be computed due to ties in the rank. So, to make sure we can proof or disproof a significant difference, we use a linear model and evaluate results.  

```{r}
model_transformed_rq2 <- lm(NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
                     data = survey_data_transformed)
summary(model_transformed_rq2)

model_outliers_rq2 <- lm(NumberOfPhysicalActivityPerWeek ~ AgeGroup, 
                     data = survey_data_no_outliers)
summary(model_outliers_rq2)
```

With the method "transformed" we almost have a significant impact of the "under" age group on physical activities per week, but the p-value is still above our threshold of `0.05`. Meaning, we need to keep the null hypothesis that we do not have a significant correlation between the number of physical activities per week and the age group.

## Evaluation

The plots in the EDA indicated, that we have a difference between age groups and that "younger" participants have more active days in a week compared to "older" ones. Statistical summaries further showed the same results as the EDA investigation. But after evaluating the significance tests, we can say that there is no significant evidence that for our second research question.  

\newpage

# Research question 3

Full-time students engage in more variety of physical activities (2+) compared to students who work.

## Exploratory Data Analysis

We load the file.

```{r file-loading}
# Load the survey data
survey_data <- read.csv("group14.csv", header=TRUE)
names(survey_data) <- c("Gender", "Age", "Studies", "NumberOfPhysicalActivityPerWeek", "TypeOfPhysicalActivity", "WorkStudy")

# Split WorkStudy into ECTS and HoursOfWork
survey_data <- separate(survey_data, "WorkStudy", c("ECTS", "HoursOfWork"), sep=";")

# Fix comma seperated numbers like 17,5 to 17.5 in order to not create NA values
survey_data$ECTS <- as.numeric(str_replace(survey_data$ECTS, ",", "."))
survey_data$ECTS <- survey_data$ECTS %>%
  replace(is.na(.), 0)

survey_data$HoursOfWork <- as.numeric(survey_data$HoursOfWork)

# We have 2 invalid inputs, "not often" and "Sunday", both resulting in a NA
# "Sunday" will be translated to 1, as we can assume, that if the person did sports more than once a week, they would
# have input more days
# However, not often is too weak to make a correct assumptions, which we therefor delete the entry
survey_data$NumberOfPhysicalActivityPerWeek <- str_replace(survey_data$NumberOfPhysicalActivityPerWeek, "Sunday", "1")
survey_data$NumberOfPhysicalActivityPerWeek <- as.numeric(survey_data$NumberOfPhysicalActivityPerWeek)
survey_data <- survey_data %>%
  filter(!is.na(NumberOfPhysicalActivityPerWeek))

# 1 ECTS = 25 Hours, Approximately 16 weeks per semester
survey_data$WeeklyHours <- survey_data$HoursOfWork + ((survey_data$ECTS*25)/16)

r3_data <- survey_data %>%
  select(NumberOfPhysicalActivityPerWeek, TypeOfPhysicalActivity, HoursOfWork)
```

In order to answer R3 we need to define who is a Full-time student and who is a Working student.

```{r student-types}
r3_data <- r3_data %>%
  mutate(Category = if_else(HoursOfWork==0, "Full-Time Student", "Working Student"))

r3_data %>%
  ggplot(aes(x=Category, fill=Category)) +
  geom_histogram(stat = "count") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.2, size = 5) +
  labs(
    title = "Number of Full-Time Students and Working Students",
    x = "Category",
    y = "Count"
  ) +
  theme(legend.position = "none")
```
Since the comparison between Full-Time Students and Working Students is not very balanced, we try to create sub groups to make the comparison groups more clear.

```{r sub-category}
r3_data <- r3_data %>%
  mutate(SubCategory = case_when(
    HoursOfWork == 0 ~ "0",
    0 != HoursOfWork & HoursOfWork <= 10 ~ "1-10h",
    10 < HoursOfWork & HoursOfWork <= 20 ~ "11-20h",
    20 < HoursOfWork & HoursOfWork <= 30 ~ "21-30h",
    30 < HoursOfWork ~ "30h+"
  ))

r3_data %>%
  ggplot(aes(x=SubCategory, fill=SubCategory)) +
  geom_histogram(stat = "count") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.2, size = 5) +
  labs(
    title = "Number of students based on SubCategory",
    x = "SubCategory",
    y = "Count"
  ) +
  theme(legend.position = "none")
```
In addition we need to extract the different activities to sum up the amount of different physical activities each person is performing.

```{r physical-variety}
types_of_physcial_activity <- c("StrengthTraining", "Cardio", "RecreationalActivities", "BallSports", "FlexibilityAndMobilit", "MartialArt", "Other")

r3_data <- r3_data %>%
  mutate(StrengthTraining = if_else(str_detect(TypeOfPhysicalActivity, "Strength Training"), 1, 0),
         Cardio = if_else(str_detect(TypeOfPhysicalActivity, "Cardio"), 1, 0),
         RecreationalActivities = if_else(str_detect(TypeOfPhysicalActivity, "Recreational Activities"), 1, 0),
         BallSports = if_else(str_detect(TypeOfPhysicalActivity, "Ball Sports"), 1, 0),
         FlexibilityAndMobilit = if_else(str_detect(TypeOfPhysicalActivity, "Flexibility and Mobilit"), 1, 0),
         MartialArt = if_else(str_detect(TypeOfPhysicalActivity, "Martial Art"), 1, 0),
         Other = if_else(str_detect(TypeOfPhysicalActivity, "Other"), 1, 0)
         ) %>%
  select(-TypeOfPhysicalActivity)

r3_data <- r3_data %>%
  mutate(NumberOfDifferentActivity = rowSums(r3_data[, types_of_physcial_activity]))

```

## Descriptive Inference

We calculate the mean of the number of different activity to compare the results for R3.

```{r mean-full-working}
r3_data %>%
  group_by(Category) %>%
  summarize(
    MeanNumberOfDifferentActivity=mean(NumberOfDifferentActivity)
  )

r3_data %>%
  group_by(SubCategory) %>%
  summarize(
    MeanNumberOfDifferentActivity=mean(NumberOfDifferentActivity)
  )
```

## Analytic Inference

At first we check if our data has normal distribution.

```{r}
shapiro.test(
  r3_data$NumberOfDifferentActivity[r3_data$Category == "Full-Time Student"])

shapiro.test(
  r3_data$NumberOfDifferentActivity[r3_data$Category == "Working Student"])
```

Since it is not, we can use the Mann-Whitney/Wilcoxon test to check if we can accept or reject our H0.

H0 - There is no significant difference in the number of physical activity between full-time students and working students.
H1 - There is significant difference in the number of physicial activity between full-time students and working students.

A value of < 0.05 means that we can reject the null hypotheses and accept our R3.

```{r}
p_value_base <- wilcox.test(NumberOfDifferentActivity ~ Category, data = r3_data)
p_value_base
```
Since the value is above 0.05, we can't reject H0, meaning that R3 is rejected.

However, we already created subcategories to further specify the working students group to see, if there is a subgroup, for which the R3 holds.

```{r}
r3_data$SubCategory <- as.factor(r3_data$SubCategory)

r3_group1 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="1-10h")

r3_group2 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="11-20h")

r3_group3 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="21-30h")

r3_group4 <- r3_data %>% 
  filter(SubCategory=="0" | SubCategory=="30h+")

p_value_group1 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, data = r3_group1, exact = TRUE)
p_value_group2 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, data = r3_group2, exact = TRUE)
p_value_group3 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, data = r3_group3, exact = TRUE)
p_value_group4 <- wilcox.exact(NumberOfDifferentActivity ~ SubCategory, data = r3_group4, exact = TRUE)

df <- data.frame(
  Group = c("Full-Time Student vs. Working Student", "1-10h", "11-20h", "21-30h", "30h+"),
  p_value = c(p_value_base$p.value, p_value_group1$p.value, p_value_group2$p.value, p_value_group3$p.value, p_value_group4$p.value)
)

df
```

We can see that only one group rejects the null hypothesis. If we can compare full-time students with students working more than 30h we can see a significant difference in the number of different physical activities.

...


